### 2017-10-09 manuscript.rmd
fixed parsing errors
revised code to mend lines with extra spaces, resolves #1. PDF not yet reexecuted

	# Parse the tree annotations, these are lines that start with SEQ
	# These have the species names, which are not in the trees themselves
	tip_annotations = 
		lines[ grepl( "^SEQ", lines, perl = TRUE ) ] %>%	# Get lines that start with SEQ
		str_c( collapse="\n" ) %>%												# Combine them into one string
		read_delim( delim=" ", col_names = FALSE ) %>% 		# Read string as tibble
		select( 2, 8 ) %>%																# Select the columns with species and gene ID
		rename( Ensembl.Gene.ID = X8 ) %>%
		rename( species = X2 )

>>>>

	# Parse the tree annotations, these are lines that start with SEQ
	# These have the species names, which are not in the trees themselves
	tip_annotations = 
		lines[ grepl( "^SEQ", lines, perl = TRUE ) ] %>%	# Get lines that start with SEQ
	  str_replace( " \\(\\d+ of \\d+\\)", "" ) %>%      # Remove instances of '(1 of 2)' and '(2 of 2)'
	  str_replace( "(([^ ]+ ){8})([^ ]+) ([^ ]+)", "\\1\\3_\\4" ) %>%      # Get rid of spaces in last field of some entries
		str_c( collapse="\n" ) %>%												# Combine them into one string
		read_delim( delim=" ", col_names = FALSE ) %>% 		# Read string as tibble
		select( 2, 8 ) %>%																# Select the columns with species and gene ID
		rename( Ensembl.Gene.ID = X8 ) %>%
		rename( species = X2 )
